---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Aman"
date: "September 25, 2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r}
install.packages("magrittr")
install.packages("tidyverse")
install.packages("tidymodels")
install.packages("gt")
install.packages("gtExtras")
install.packages("DataExplorer")
```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

The `the_tate` dataset has \_\_\_ unique artists who worked from \_\_\_ to \_\_\_. The works were acquired between the years \_\_\_ and \_\_\_.

```{r}
the_tate_area <- the_tate[!is.na(the_tate$width) & !is.na(the_tate$height),]
area <- the_tate_area$width * the_tate_area$height
the_tate_area <- cbind(the_tate_area, area)
the_tate_area <- the_tate_area[order(the_tate_area$area),]
```

```{r}
library(dplyr)
the_tate_by_artist <- the_tate %>%
  group_by(artist) %>%
  summarize(count = n())
the_tate_by_artist <- the_tate_by_artist[order(-the_tate_by_artist$count),]
head(the_tate_by_artist)
```

```{r}
summarize(the_tate)
```

```{)}
```

```{r}
the_tate %>% summary()
```

```{r}
summarize(the_tate)%>%
```

```{r}
library(dplyr)
library(DataExplorer)

general_observations <-the_tate %>%
  summarize(
    UniqueArtists = n_distinct(artist),
    PeriodRepresented = paste(min(date),"to", max(date)),
    acquisitionYear = paste(min(acquisitionYear), "to", max(acquisitionYear))
  )

print(general_observations)

introduce(tate_collection)
plot_missing(tate_collection)
```

### Exercise 2

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

```{r}
dplyr:: distinct(artist)
```

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
